---
title: "Module2_rmd1"
author: "Jaqueline"
date: "2022-10-13"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# This is a level 1 hearder
## R Markdown
### This is a lever 3 hearder

This is an _R Markdown_ document. **Markdown** is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
[GOOGLE](https://www.google.com/)

```
When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:
```

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

```{r pressure2, echo=FALSE, fig.height=4, fig.width=4, warning=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Insert tables
```{r}
knitr::kable(head(cars),
             caption = "Top six rows of Cars Dataset")
```


## Insert a equation

$$ Y = \beta_0 + \beta_1x $$